14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-10 rules/rules19.tex
Added industrial and model validating track.

>>>>

\subsection{Industry challenge track}
\label{sec:exec:industry-challenge}

The industry challenge track will follow the same rules as the single problem track,
with two exceptions: benchmark selection and the time limit. The track will run on
all SMT-LIB benchmarks that have an unknown status and that have been tagged as being
 \emph{industrial}. Additionally we will include benchmarks nominated by the community.
\lh{TODO: benchmark selection still needs discussion}
\lh{TODO: We didn't decide on what we do if only one solver gives an answer and we don't
know if the problem is sat/unsat}

\subsection{Model Validation Track (experimental)}
\label{sec:exec:model}
The model validation track will evaluate the solver's ability to produce models
for satisfiable problems. This track will run on all QF\_BV satisfiable benchmarks
from the single problem track.

The SMT-LIB language accommodates this functionality by providing the ability to
request a satisfying model after a \akey{check-sat} command returns \texttt{sat}.
The satisfiable core that is returned must consist of definitions specifying all
and only the current user-declared function symbols, in the format prescribed by
the SMT-LIB standard.

The result of a solver is considered erroneous if the response to the
\akey{checks-sat} command is \texttt{unsat}, if the returned model is not
well-formed (e.g. does not provide a definition for all the user-declared function
symbols), or if the returned model does not satisfy the benchmark.

In order to check that the model satisfies the benchmark, the organizers will use
a model validating tool. The organizers will make this tool available to solver
developers before the solver submission deadline.
